---
title: "Introduction to SA24168406-package"
author: "SA24168406"
date: "2024-12-07"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SA24168406-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction
This R package has 2 R functions named My_kmeans_plusplus and My_aco and 2 Rcpp functions named My_stratified_samplingC and Gibbs_chain_C. What's more, this package includes all my homework answers in Homework.Rmd file. The following is a detailed description of the use of the four functions with examples.

### My_kmeans_plusplus function
This function calculates the centers of K-mean++ cluster and show the clustering results by a figure using R. It has 3 input parameters including data(the data for clustering), k(the number of the centers), max_iter(the maximum number of iterations for clustering, the default value is 100), and returns a list of the centers and clusters. The following is an example:
```{r}
library(SA24168406)
set.seed(123)
data <- matrix(rnorm(100 * 2), nrow = 100)
k <- 3
result <- My_kmeans_plusplus(data, k)
print(result$centers)
print(result$clusters)
```

### My_aco function
This function calculates the best path with ACO algorithm and show the iterative process by a figure using R. It has 7 input parameters including cities(the coordinates of the cities), AntsNum(the number of the ants), max_iter(the maximum number of iterations for optimizing, the default value is 100), alpha(the pheromone factor), beta(the heuristic factor), rho(the pheromone volatile factor), Q(the pheromone increment), and returns a list of the optimal path in each iteration and its length and the best path with its length. The following is an example:
```{r}
library(SA24168406)
set.seed(123)
n <- 20
alpha <- 1
beta <- 2
rho <- 0.5
Q <- 100
AntsNum <- 10
max_iter <- 100
cities <- data.frame(x = runif(n, min = 0, max = 100),
                     y = runif(n, min = 0, max = 100))
result <- My_aco(cities, AntsNum, max_iter, alpha, beta, rho, Q)
print(result$min_bestPath)
print(result$min_bestLength)
plot(
  result$bestLength,
  type = "l",
  main = "蚁群算法用例",
  xlab = "迭代次数",
  ylab = "最佳路径长度"
)
```

### My_stratified_samplingC Rcppfunction
This function implements stratified sampling with 2 input parameters including data(the data that contains the id, category, and value columns), samplesPerCategory(the number of samples for each category) and returns a list of the sampling results including id and category. The following is an example:
```{r}
library(Rcpp)
data <- data.frame(id = 1:9, category = rep(c("A", "B", "C"), each = 3), value = rnorm(9))
samples_per_category <- list(A = 1, B = 2, C = 1)  # 每个类别的样本数量
sampled_data <- My_stratified_samplingC(data, samples_per_category)
sampled_data
```

### Gibbs_chain_C Rcppfunction
This function implements Gibbs sampling with 7 input parameters including a,b,n(parameters of the objective density function), N(the number of samples generated), burn(the number of samples discarded), x0(the initial x-value), y0(the initial y-value) and returns Gibbs samples. The following is an example:
```{r}
set.seed(12345)
N <- 1e4
burn <- 1000
a <- 2
b <- 4
n <- 16
x0 <- sample(0:n,1)
y0 <- runif(1)
xC <- Gibbs_chain_C(a, b, n, N, burn, x0, y0)
```
